%-------------------------
% Resume in Latex
% Author : Aras Gungore
% Edited By: Shakil Ahmed
% License : MIT
%------------------------


\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------


% Define custom icon styles
\newcommand{\iconcolor}{blue} % Change the color here
\newcommand{\iconsize}{1.2em} % Change the size here
\begin{center}
    \textbf{\Huge \scshape Md Shakil Ahmed} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.9pt} \href{tel:8801682523401}{+880 130 846 6291}
    $|$
    \faAt \hspace{.3pt} \href{mailto:ahmedmshakil1@gmail.com}{ahmedmshakil1@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.3pt} \href{https://www.linkedin.com/in/ahmedmshakil/}{LinkedIn}
    $|$
    \faGithub \hspace{.3pt} \href{https://github.com/ahmedmshakil}{GitHub}
    $|$
    \faGlobe \hspace{.3pt} \href{https://ahmedmshakil.netlify.app/}{Portfolio}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://maps.app.goo.gl/yXjbz1LHBvWixLsa6}{Dhaka, Bangladesh}
\end{center}


%----------- Summary -----------

\section{Summary}
  \vspace{4pt}
  \resumeSubHeadingListStart
 {A Computer Science and Engineering student from Independent University, Bangladesh who is Self-motivated, highly passionate  for the technology and possesses a strong interest in researching data science, Natural language processing and machine learning in the hopes of making a substantial impact on the field.}
  \resumeSubHeadingListEnd


%----------- Summary -----------

\section{Research Interests}
  \vspace{4pt}
  \resumeSubHeadingListStart
 {Data Science, Machine Learning, Natural Language Processing, Image Processing, Bioinformatics, Blockchain, Software Engineering, System Design}
   \resumeSubHeadingListEnd



%----------- EDUCATION -----------

\section{Education}
  \vspace{4pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Independent University, Bangladesh
      % \normalfont{(Admission rate: 0.09\%)}
      }{Dhaka, Bangladesh}
      {B.Sc. in Computer Science and Engineering;   \textbf{}}{January 2021 \textbf{--} December 2024}
    \textbf{Ongoing} {Thesis: credit risk rating system using Blockchain}

        \resumeItemListStart
             \resumeItem{\textbf{Relevant coursework:} Calculus I-II, Differential Equations, Digital System Design,Data Structure, Algorithms, Object Oriented Programming, Database Management System, Distributed Database System}
         \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
        
    \resumeSubheading
      {Independent University, Bangladesh}{Bashundhara R/A, Dhaka, Bangladesh }
      {Undergraduate Teaching Assistant}{Jan 2023 \textbf{--} Sep 2023}
        \resumeItemListStart
            \resumeItem{\textbf{Courses Taught:} Structured Programming (Programming language: Python), Database Management.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Klatch Technologies}{Assam, India (Remote)}
      {AI Research and Development Intern}{Oct 2023 \textbf{--} Dec 2023}
        \resumeItemListStart
            \resumeItem{Implemented common NLP tasks using transformers such as named-entity recognition (NER), part-of-speech (POS) tagging, sentiment analysis, text classification, and extractive/generative question answering.}
            \resumeItem{Intent-based Query Model for Question Answering}
            \resumeItem{Worked on a custom Medical domain question-answering system by fine-tuning a BERT base model transformer. Evaluated the exact match and F1 scores using different Medical data sets and compared the evaluation results.}
        \resumeItemListEnd
    \resumeSubheading
      {Student Tutor}{Uttara, Dhaka, Bangladesh (Part-time)}
      {Teacher}{Feb 2020 \textbf{--} present}
        \resumeItemListStart

            \resumeItem{Work with students, and indoctrinate them about problems they are having with the course material.}
            \resumeItem{Holding 15 hours per week's tution hours.}
            \resumeItem{Lead discussion sessions with students.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

  
%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{4pt}
  {\textbf{Research On going}
  \vspace{30pt}
  





%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
    
        \textbf{Ahsanullah Master Smriti Scholarship:}{ Awarded to the 9th and 17th place twice(2008, 2009) for outstanding performance among Gazipur District at Primary Level Scholarship Exam.} \\ \vspace{3pt}
         \textbf{Best Athelate Award:}{ Awarded to the Champion price twice(2014, 2016) for securing three 1st place in the Annual sports competition in UHSC  } \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Invoice Generator Using Python } $|$ \emph{\href{https://github.com/ahmedmshakil/Invoice_Generator}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{In this project, I create a real time invoice generator using python to generate automated shopping invoice. }
          \resumeItemListEnd
      
         
                \resumeProjectHeading
        {\textbf{Student Performance Monitoring Syatem 2.0 for IUB} $|$ \emph{\href{https://github.com/ahmedmshakil/spms2.0}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{This is the database management project that we implement graphs and charts for the all users those who using iras.}
            \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{Hotel Management System Covid-19} $|$ \emph{\href{https://github.com/ahmedmshakil/The-hotel-management-system-Covid-19}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Real-time Employee management system object and Face Recognition using RCNN, Redis Docker, Django}
            \resumeItem{Manage category of room, Health care, and payment. Based on the customer's situation suggest a hospital}
          \resumeItemListEnd
      
      
      
      
    \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming:}{ C++, Java, Python, JavaScript, MATLAB, SQL, MySQL} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Git,Github, Gitlab, GitKraken, OpenCV} \\ \vspace{3pt}
        
        \textbf{Languages:}{ Bangla (Native), English (Professional),  French (Elementary)}
        
        % \textbf{Frameworks}{: X, X, X} \\
        % \textbf{Developer Tools}{: X, X, X} \\
        % \textbf{Libraries}{: X, X, X} \\
        % \textbf{Applications}{: X, X, X}
    }}
  \resumeSubHeadingListEnd


\section{Competitive Programming}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Problem-Solving: } {Solved numerous data structure and algorithmic problems and participated in online programming contests in various online judges including Codeforces, Codechef and Atcoder.} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd

%----------- RELEVANT COURSEWORK -----------





%----------- CERTIFICATES -----------





%----------- ORGANIZATIONS -----------




%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Table Tannis, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------





%-------------------------------------------
\end{document}